A space-time \skewt model for threshold exceedances

### 2016-12-09 LaTeX/response_2.tex

\documentclass[11pt]{article}
\usepackage[letterpaper, margin=1in]{geometry}
% \documentclass[useAMS,usenatbib,referee]{biomweb}
\usepackage{amssymb, amsthm, amsmath}
\usepackage{amssymb, amsmath}
\usepackage{bm}
\usepackage{graphicx}
\usepackage[authoryear]{natbib}
\usepackage{bm}
\usepackage{verbatim}
\usepackage{lineno}
\usepackage{soul}
\usepackage{color}
% \usepackage{enumitem}
\usepackage{enumerate}
\usepackage{setspace}
\usepackage{appendix}
% \usepackage{caption}
% \captionsetup[table]{name=Web Table}

% cross-referencing appendices
\usepackage{xr}
\externaldocument{skewt_rev}
\externaldocument{supplemental_rev}

% \usepackage[left=1in,top=1in,right=1in]{geometry}
% \pdfpageheight 11in
% \pdfpagewidth 8.5in
% \linespread{2.0}
\input{mycommands.sty}
\begin{document}

\begin{center}
Point-by-Point response to Report on revised manuscript\\
Biometrics MS \#150926M\\
\today
\end{center}

Again, we wish to thank the reviewers and editors for their helpful comments and feedback regarding our manuscript. 
To address the concerns, we edited the manuscript to address the concerns given in the revised report.

\section*{Response to the comments of the Associate Editor}
\subsection*{Remaining comments}
\begin{enumerate}[1.]
	\item p.2 1.1-2: ``Asymptotic \ldots level'' this sentence doesn't make sense

	\begin{response}
	We have changed this sentence to read ``Asymptotic dependence/independence are notions which describe the probability that two random variables simultaneously exceed an extremely high level.''
	\end{response}

	\item p.6 Section 3.2 1.2: space missing after .

	\begin{response}
	We have added a space after the `.'
	\end{response}

	\item p.7 Figure 2: is this really an \emph{estimate} of $\chi(h)$; are these not theoretical values?

	\begin{response}
	We have changed the wording on p.7 (2 lines above the suggested location of Figure 2) text describing Figure 2 from ``we estimate $\chi(h)$ \ldots'' to ``we show $\chi(h)$ \ldots''.
	\end{response}

	\item The phrasing ``we use a transformation of a Gaussian random variable on $z_t$\ldots'' sounds quite strange. Why not just say ``we transform $z_t$ to the Gaussian scale using the probability integral transform''? And similarly for $\sigma^2_t$.

	\begin{response}
	We have adopted the wording suggested by the reviewer.
	\end{response}

	\item p.7 Section 4.1: What method do you use to simulate from the truncated multivariate Gaussian - rejection? It would be useful to give an idea of how difficult or otherwise this step is.

	\begin{response}
	We have added clarification that we use the conditional normal distribution to sample from the univariate truncated normal distribution.
	\end{response}

	\item p.11 Section 5.1 / Fig. 3: the title of the 4th panel in Figure 3 is ``Asymmetric logistic'' whereas (4) in 5.1 is ``Reich and Shaby'' process

	\begin{response}
	We have changed the title of the plot to ``Reich and Shaby'' to be consistent with the text.
	\end{response}

	\item p.11 1-2. \texttt{rmaxstab}

	\begin{response}
	This has been corrected.
	\end{response}

	\item p.12 item (5) typo ``max-table''

	\begin{response}
	This has been corrected.
	\end{response}

	\item p.15 Section 6.1: when giving the burn in period of 25,000, is this taken out of the 30,000 iterations, or in addition to them?

	\begin{response}
	We have adjusted the wording (as well as the corresponding part of the simulation study in 5.1) here to reflect that the burn-in period is taken out of the number of iterations reported.
	\end{response}

	\item Web Appendix C, p.6 final line: typo "Poission"; p.7 eq.(3) typo $>=$

	\begin{response}
	These have been corrected.		
	\end{response}

\end{enumerate}
\bibliographystyle{biom}
\bibliography{library}

\end{document}

### 2016-12-09 LaTeX/skewt_rev_2.tex
edits for final submission

% cross-referencing appendices
\usepackage{xr}
\externaldocument{supplemental_rev}

@@

A spatial model for threshold exceedances warrants special consideration and standard spatial methods are likely to perform poorly.
First, because we are interested only in high values, we want to ``let the tail speak for itself''.
That is, if we fit a model to the entire data set, low-to-moderate values would influence the fit of the overall model.
As there are more of these values, they can unduly influence the distribution at the higher levels about which we are interested.
Our inference method will only use data which exceed a pre-selected threshold and will censor data below the threshold, thereby tailoring the fit to the levels of interest.
Second, likelihood-based spatial modeling typically assumes a Gaussian process, which is appropriate when mean behavior is of interest.
However, the Gaussian distribution is light-tailed and symmetric, and therefore may be inappropriate for modeling data which does not share this tail behavior.
Third, we aim to capture the dependence structure when ozone is at high levels, and dependence at these levels may not be well-represented by covariances which focus again on mean behavior.
Asymptotic dependence/independence (see \sref{sts:extdep}) are notions which describe how two random variables' probability of simultaneous exceedance of an extremely high level.
The Gaussian distribution always exhibits asymptotic independence, except in the case of perfect dependence, thus is an inappropriate model for data which exhibits asymptotic dependence.
To allow for more flexibility in the marginal tail and to allow for asymptotic dependence, the \skewt distribution forms the basis for our model.

@@

\subsection{Partitioning to remove long-range asymptotic dependence}\label{sts:part}
For a large spatial domain, it may not be reasonable to assume sites that are far apart demonstrate asymptotic dependence.%, so we handle the problem of long-range asymptotic dependence with a random partition.
% Modeling different levels of asymptotic dependence was discussed by \citet{Wadsworth2012}.
% \citet{Huser2014} also allow for varying asymptotic dependence across both space and time with a partition structure represented by random discs moving across the space for a random duration with a random velocity and random radius.
As discussed in \sref{sts:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site using a partitioning approach.
The model becomes
\begin{align} \label{steq:partition}
  Y(\bs) &= \bX(\bs)^\top \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{steq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
In other words, $P_k$ is composed of all sites for which the closest knot is $\bw_k$.
For all $\bs \in P_k$, with $k = 1, 2, \ldots, K$, the functions $z(\bs)$ and $\sigma(\bs)$ are equal to the constants $z_k$ and $\sigma_k$ respectively, and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2_k \iid$ IG$(a / 2, b / 2)$.
So, within each partition, $Y(\bs)$ follows the spatial \skewt process defined in \sref{sts:spatialskew}.
Across partitions, the $Y(\bs)$ remain dependent via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.
However, the bivariate distribution for sites in different partitions is neither Gaussian nor \skewt and does not have asymptotic dependence.

The partitioning model removes long-range dependence.
Conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs_1$ and $\bs_2$ in partitions $k_1$ and $k_2$ respectively is
\begin{align}
  \chi(h) &= I(k_1 = k_2) \chi_{\text{skew-}t}(h) \label{steq:chiskewt}
\end{align}
where $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a \skewt process given in equation \eref{steq:chiskew-t} of \aref{sta:skewt}, and $h = ||\bs_1 - \bs_2||$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where \mbox{$\pi(h) = \Pr(k_1 = k_2)$} is the probability that two sites separated by distance $h$ are in the same partition.
In \aref{sta:proofsamepartition}, we show that assuming the knots follow a homogeneous Poisson process, $\lim_{h \rightarrow \infty} \pi(h) = 0$, and thus long-range dependence is removed.
% In \aref{sta:proofsamepartition}, we show that $\lim_{h \rightarrow \infty} \pi(h) = 0$, assuming that the knots follow a homogeneous Poisson process.
% This implies that $\lim_{h \rightarrow \infty} \chi(h) = 0$.
In practice we fix $K$ at a finite value and use a uniform distribution for the knots $\bw_1, \ldots, \bw_K$.
In \fref{stfig:chi}, we estimate $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a \skewt distribution with $\alpha = 10$, and 3 degrees of freedom.
% In \fref{stfig:chi} we estimate $\pi(h)$ through simulation.
% To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
% We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
% For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
% This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{plots/chi-h.pdf}
  \caption{Extremal dependence measure $\chi(h)$, as a function of distance, $h$, for $K = 1, 3, 5$, and $10$ knots.}
  \label{stfig:chi}
\end{figure}

@@

We use an AR(1) time series model for $\bw_{tk}$, $z_{tk}$, and $\sigma_{tk}$.
The time series model must be specified after a transformation to preserve the \skewt process at each time point.
For each time-varying parameter, we transform the parameter to obtain a standard normal marginal distribution, place a Gaussian prior with autocorrelation on the transformed parameter, and then transform back to the appropriate marginal distribution for the \skewt process.
We first transform the spatial knots from $\calD$ to $\calR^2$ as follows.
Let
\begin{align} \label{steq:wstar}
  w^*_{tki} = \Phi^{-1}\left[ \frac{ w_{tki} - \min(\bs_i)}{ \max(\bs_i) - \min(\bs_i) } \right], \quad i = 1, 2
\end{align}
where $\Phi$ is a univariate standard normal density function and $\bs_i = [s_{1i}, \ldots, s_{ni}]$.
Then the transformed knots $\bw^*_{tk} \in \calR^2$.
We use a transformation of a Gaussian random variable on $z_{t}(\bs)$ to ensure that the marginal distributions of $z_t(\bs)$ are half-normal.
Let
\begin{align} \label{steq:zstar}
  z^*_t(\bs) = \Phi^{-1}\left\{ \text{HN}[z_t(\bs)] \right\}
\end{align}
where HN is the distribution function of a half-normal random variable.
We also use a transformation of a Gaussian random variable on $\sigma^2_t(\bs)$ to ensure that the marginal distributions of $\sigma^2_t(\bs)$ are inverse gamma.
Let
\begin{align} \label{steq:sigmastar}
  \sigma^{2*}_t(\bs) =\Phi^{-1}\left\{ \text{IG}[\sigma^2_t(\bs)] \right\}
\end{align}
where IG is defined as before.
The AR(1) process for each tail parameter is $\bw^*_{1k} \sim N_2(\bZero, \bI_2)$ where $\bI_2 = \text{diag}(1, 1)$, $z^*_{1k} \sim N(0, 1)$, $\sigma^{2*}_{1k} \sim N(0, 1)$, and for $t > 1$ the time series is modeled as
\begin{align}
  \bw^*_{tk} | \bw^*_{t-1, k} &\sim N_2\left[\phi_w \bw^*_{t-1, k}, (1 - \phi_w^2) \bI_2 \right] \label{steq:ts-wstar}\\
  z^*_{tk} | z^*_{t-1, k} &\sim N \left[\phi_z z^*_{t-1, k}, (1 - \phi_z^2)\right] \label{steq:ts-zstar} \\
  \sigma^{2*}_{tk} | \sigma^{2*}_{t-1, k} &\sim N \left[\phi_\sigma \sigma^{2*}_{t-1, k}, (1 - \phi_\sigma^2) \right] \label{steq:ts-sigmastar}
\end{align}
where $|\phi_w|$, $|\phi_z|$, $|\phi_\sigma| < 1$.
These are stationary time series models with marginal distributions \hbox{$\bw^*_{k} \sim N_2(\bZero, \bI_2)$} \hbox{$z^*_{k} \sim N(0, 1)$}, and \hbox{$\sigma^{2*}_{k} \sim N(0, 1)$}.
After transformation back to the original space, $\bw_{tk} \sim \text{Unif}(\calD)$, $z_{tk} \sim $ HN$(0, 1)$, and $\sigma^2_{tk} \sim \text{IG}(a / 2, b / 2)$.
We then create the partition for day $t$ using $\bw_{t1}, \ldots, \bw_{tK}$.
For each day, the model is identical to the spatial-only model in \eref{steq:partition} by construction.

@@

\subsection{Computation}\label{sts:comp}
We use MCMC methods to estimate the posterior distribution of the model parameters.
At each MCMC iteration, we first impute values below the threshold conditional on observations above the threshold.
% This is feasible for large datasets with our model because for a single day, conditional on the model parameters, we only need to draw from a truncated multivariate normal distribution.
% We can use Gibbs sampling to update $Y_t(\bs)$ for censored observations that are below the threshold $T$.
After conditioning on $\lambda$, $z_t(\bs)$ and non-censored observations, $Y_t(\bs)$ has truncated normal full conditionals $Y_t(\bs) \sim N_{(-\infty, T)}(\bX_t^\top(\bs) \beta + \lambda | z_t(\bs)|, \bSigma)$.

@@

\subsection{Design}\label{sts:simdesign}
For all simulation designs, we generated data from model \eref{steq:partition} in \sref{sts:part} using $n_s=144$ sites and $n_t=50$ independent days.
The sites were generated uniformly on the square $[0, 10] \times [0, 10]$.
We generated data from five different simulation designs:
\begin{enumerate}[leftmargin=3em]
  \item Gaussian, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=5$ knots
  \item \Skewt, $K=1$ knots
  \item \Skewt, $K=5$ knots
  \item \citet{Reich2012} max-stable process %with GEV(1, 1, 0.2) marginals with dependence parameteter $\gamma_{\text{AL}} = 0.5$
  % \item Transformation below $T = q(0.80)$
  \item Brown-Resnick max-stable process \citep{Kabluchko2009} %with unit Fréchet marginals and stable semivariogram with range 1 and smoothness 0.5
\end{enumerate}
In the first three designs, the realizations from $v_t(\bs)$ were generated using a \Matern covariance with smoothness parameter $\nu = 0.5$, spatial range $\varphi = 1$ and $\gamma = 0.9$.
In the first design, $\sigma^2 = 2$ was used for all days which results in a Gaussian distribution.
For designs 2 and 3, $\sigma^2_{tk} \iid \text{IG}(3, 8)$ to give a $t$ distribution with 6 degrees of freedom.
For design 1, we set $\lambda = 0$.
For designs 2 and 3, $\lambda = 3$ was used as to simulate moderate skewness, and the $z_t$ were generated as described in \sref{sts:part}.
In designs 1 -- 3, the mean $\bX^\top \bbeta = 10$ was assumed to be constant across space.
In the fourth design, we generated from the max-stable model of \citet{Reich2012}.
The marginal distributions follow a generalized extreme value distribution with location parameter 1, scale parameter 1, and shape parameter 0.2.
Spatial dependence in the form an asymmetric logistic dependence function is induced by random effects for kernel basis functions associated with 144 spatial knots defined on a square grid on $[1,9] \times [1,9]$.
We set the dependence parameter ($\alpha$ in Reich and Shaby, 2012) to 0.5 which represents moderate spatial dependence.
For the final design, we generated data from a Brown-Resnick max-stable process  using \texttt{rmaxtab} in the \texttt{SpatialExtremes} package of \texttt{R} \citep{Ribatet2015}.
For this design we fixed unit \Frechet margins, and we used a range of 1 and smoothness 0.5.
% In the final design, we generate $\tilde{y}$ using the setting from design 2, and then transform the data
% \begin{align}
%   y = \left\{ \begin{array}{lc}
%     \tilde{y}, \quad & \tilde{y} > T \\[0.5em]
%     T \exp\{\tilde{y} - T\}, \quad & \tilde{y} \le T
%   \end{array}\right.
% \end{align}
% where $T = q(0.80)$ is the 80th sample quantile of the data.
% The final design is included to explore the importance of using a threshold exceedance model when the distribution for the bulk of the data is misspecified.

$M = 50$ data sets were generated for each design.
For each data set we fit the data using six models
\begin{enumerate}[leftmargin=3em]
  \item Gaussian marginal, $K=1$ knots
  \item \Skewt marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item \Skewt marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
  \item \citet{Reich2012} max-table model thresholded at $T = q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
All methods were fit using a fully-Bayesian approach that simultaneously estimates marginal and spatial dependence parameters.
The design matrix $\bX$ includes an intercept with a first-order spatial trend with priors of $\beta_\text{int}$, $\beta_\text{lat}$, $\beta_\text{long},  \iid \text{N}(0, 10)$ although only the intercept is used in the data generation.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\varphi \sim \text{Unif}(0, 15)$.
The skewness parameter has prior $\lambda \sim N(0, 20)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(a / 2, b / 2)$, where $a$ has a discrete uniform prior on a mesh from $0.2$ to $20$ with spacing of $0.1$ and $b$ has a Gamma$(0.1, 0.1)$ prior.
As described in \sref{sts:skewt}, these priors are meant to be fairly uninformative to allow the data to dictate both the degrees of freedom $a$ and precision $b$ of the process.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We tried also fitting the \skewt marginals for the thresholded models, but it is very challenging for the MCMC to properly identify the skewness parameter with a censored left tail.
Each chain of the MCMC ran for 20,000 iterations with a burn-in period of 10,000 iterations.
Although the goal of this simulation study is not to assess parameter estimation, for design (2) and method (2) where data are generated and fit with a \skewt distribution, the samples converges for $\lambda$ and $a$, and the empirical coverage of posterior 95\% intervals is near the nominal level (96\% coverage for $\lambda$ and 90\% for $a$).
It should be noted that in the models with multiple partitions (i.e. models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC; however, we are not interested in these parameters but rather spatial predictions and tail probabilities which converge well.
Finally, we did not fit a Brown-Resnick model because we cannot use a Bayesian approach with so many sites.

@@

>>>>

% cross-referencing appendices
\usepackage{xr}
\externaldocument{supplemental_rev_2}

@@

A spatial model for threshold exceedances warrants special consideration and standard spatial methods are likely to perform poorly.
First, because we are interested only in high values, we want to ``let the tail speak for itself''.
That is, if we fit a model to the entire data set, low-to-moderate values would influence the fit of the overall model.
As there are more of these values, they can unduly influence the distribution at the higher levels about which we are interested.
Our inference method will only use data which exceed a pre-selected threshold and will censor data below the threshold, thereby tailoring the fit to the levels of interest.
Second, likelihood-based spatial modeling typically assumes a Gaussian process, which is appropriate when mean behavior is of interest.
However, the Gaussian distribution is light-tailed and symmetric, and therefore may be inappropriate for modeling data which does not share this tail behavior.
Third, we aim to capture the dependence structure when ozone is at high levels, and dependence at these levels may not be well-represented by covariances which focus again on mean behavior.
Asymptotic dependence/independence (see \sref{sts:extdep}) are notions which describe the probability that two random variables simultaneously exceed of an extremely high level.
The Gaussian distribution always exhibits asymptotic independence, except in the case of perfect dependence, thus is an inappropriate model for data which exhibits asymptotic dependence.
To allow for more flexibility in the marginal tail and to allow for asymptotic dependence, the \skewt distribution forms the basis for our model.

@@

\subsection{Partitioning to remove long-range asymptotic dependence}\label{sts:part}
For a large spatial domain, it may not be reasonable to assume sites that are far apart demonstrate asymptotic dependence. %, so we handle the problem of long-range asymptotic dependence with a random partition.
% Modeling different levels of asymptotic dependence was discussed by \citet{Wadsworth2012}.
% \citet{Huser2014} also allow for varying asymptotic dependence across both space and time with a partition structure represented by random discs moving across the space for a random duration with a random velocity and random radius.
As discussed in \sref{sts:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site using a partitioning approach.
The model becomes
\begin{align} \label{steq:partition}
  Y(\bs) &= \bX(\bs)^\top \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{steq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
In other words, $P_k$ is composed of all sites for which the closest knot is $\bw_k$.
For all $\bs \in P_k$, with $k = 1, 2, \ldots, K$, the functions $z(\bs)$ and $\sigma(\bs)$ are equal to the constants $z_k$ and $\sigma_k$ respectively, and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2_k \iid$ IG$(a / 2, b / 2)$.
So, within each partition, $Y(\bs)$ follows the spatial \skewt process defined in \sref{sts:spatialskew}.
Across partitions, the $Y(\bs)$ remain dependent via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.
However, the bivariate distribution for sites in different partitions is neither Gaussian nor \skewt and does not have asymptotic dependence.

The partitioning model removes long-range dependence.
Conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs_1$ and $\bs_2$ in partitions $k_1$ and $k_2$ respectively is
\begin{align}
  \chi(h) &= I(k_1 = k_2) \chi_{\text{skew-}t}(h) \label{steq:chiskewt}
\end{align}
where $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a \skewt process given in equation \eref{steq:chiskew-t} of \aref{sta:skewt}, and $h = ||\bs_1 - \bs_2||$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where \mbox{$\pi(h) = \Pr(k_1 = k_2)$} is the probability that two sites separated by distance $h$ are in the same partition.
In \aref{sta:proofsamepartition}, we show that assuming the knots follow a homogeneous Poisson process, $\lim_{h \rightarrow \infty} \pi(h) = 0$, and thus long-range dependence is removed.
% In \aref{sta:proofsamepartition}, we show that $\lim_{h \rightarrow \infty} \pi(h) = 0$, assuming that the knots follow a homogeneous Poisson process.
% This implies that $\lim_{h \rightarrow \infty} \chi(h) = 0$.
In practice we fix $K$ at a finite value and use a uniform distribution for the knots $\bw_1, \ldots, \bw_K$.
In \fref{stfig:chi}, we show $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a \skewt distribution with $\alpha = 10$, and 3 degrees of freedom.
% In \fref{stfig:chi} we estimate $\pi(h)$ through simulation.
% To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
% We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
% For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
% This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{plots/chi-h.pdf}
  \caption{Extremal dependence measure $\chi(h)$, as a function of distance, $h$, for $K = 1, 3, 5$, and $10$ knots.}
  \label{stfig:chi}
\end{figure}

@@

We use an AR(1) time series model for $\bw_{tk}$, $z_{tk}$, and $\sigma_{tk}$.
The time series model must be specified after a transformation to preserve the \skewt process at each time point.
For each time-varying parameter, we transform the parameter to obtain a standard normal marginal distribution, place a Gaussian prior with autocorrelation on the transformed parameter, and then transform back to the appropriate marginal distribution for the \skewt process.
We first transform the spatial knots from $\calD$ to $\calR^2$ as follows.
Let
\begin{align} \label{steq:wstar}
  w^*_{tki} = \Phi^{-1}\left[ \frac{ w_{tki} - \min(\bs_i)}{ \max(\bs_i) - \min(\bs_i) } \right], \quad i = 1, 2
\end{align}
where $\Phi$ is a univariate standard normal density function and $\bs_i = [s_{1i}, \ldots, s_{ni}]$.
Then the transformed knots $\bw^*_{tk} \in \calR^2$.
We transform $z_{t}(\bs)$ to the Gaussian scale using the probability integral transform to ensure that the marginal distributions of $z_t(\bs)$ are half-normal.
Let
\begin{align} \label{steq:zstar}
  z^*_t(\bs) = \Phi^{-1}\left\{ \text{HN}[z_t(\bs)] \right\}
\end{align}
where HN is the distribution function of a half-normal random variable.
We also transform $\sigma^2_t(\bs)$ to the Gaussian scale using the probability integral transform to ensure that the marginal distributions of $\sigma^2_t(\bs)$ are inverse gamma.
Let
\begin{align} \label{steq:sigmastar}
  \sigma^{2*}_t(\bs) =\Phi^{-1}\left\{ \text{IG}[\sigma^2_t(\bs)] \right\}
\end{align}
where IG is defined as before.
The AR(1) process for each tail parameter is $\bw^*_{1k} \sim N_2(\bZero, \bI_2)$ where $\bI_2 = \text{diag}(1, 1)$, $z^*_{1k} \sim N(0, 1)$, $\sigma^{2*}_{1k} \sim N(0, 1)$, and for $t > 1$ the time series is modeled as
\begin{align}
  \bw^*_{tk} | \bw^*_{t-1, k} &\sim N_2\left[\phi_w \bw^*_{t-1, k}, (1 - \phi_w^2) \bI_2 \right] \label{steq:ts-wstar}\\
  z^*_{tk} | z^*_{t-1, k} &\sim N \left[\phi_z z^*_{t-1, k}, (1 - \phi_z^2)\right] \label{steq:ts-zstar} \\
  \sigma^{2*}_{tk} | \sigma^{2*}_{t-1, k} &\sim N \left[\phi_\sigma \sigma^{2*}_{t-1, k}, (1 - \phi_\sigma^2) \right] \label{steq:ts-sigmastar}
\end{align}
where $|\phi_w|$, $|\phi_z|$, $|\phi_\sigma| < 1$.
These are stationary time series models with marginal distributions \hbox{$\bw^*_{k} \sim N_2(\bZero, \bI_2)$} \hbox{$z^*_{k} \sim N(0, 1)$}, and \hbox{$\sigma^{2*}_{k} \sim N(0, 1)$}.
After transformation back to the original space, $\bw_{tk} \sim \text{Unif}(\calD)$, $z_{tk} \sim $ HN$(0, 1)$, and $\sigma^2_{tk} \sim \text{IG}(a / 2, b / 2)$.
We then create the partition for day $t$ using $\bw_{t1}, \ldots, \bw_{tK}$.
For each day, the model is identical to the spatial-only model in \eref{steq:partition} by construction.

@@

\subsection{Computation}\label{sts:comp}
We use MCMC methods to estimate the posterior distribution of the model parameters.
At each MCMC iteration, we first impute values below the threshold conditional on observations above the threshold.
% This is feasible for large datasets with our model because for a single day, conditional on the model parameters, we only need to draw from a truncated multivariate normal distribution.
% We can use Gibbs sampling to update $Y_t(\bs)$ for censored observations that are below the threshold $T$.
After conditioning on $\lambda$, $z_t(\bs)$ and non-censored observations, $Y_t(\bs)$ has truncated normal full conditionals $Y_t(\bs) \sim N_{(-\infty, T)}(\bX_t^\top(\bs) \beta + \lambda | z_t(\bs)|, \bSigma)$.
To impute the censored observations, at each MCMC iteration, for censored site $i$ and day $t$, we use the conditional distribution of $\widetilde{Y}_t(\bs_i)$ given the current imputed values for all censored sites and true values for all non-censored sites $\widetilde{Y}^{(c)}_t(\bs_{-i})$.
Conditional on $\widetilde{Y}^{(c)}_t(\bs_{-i})$, the imputation of $\widetilde{Y}_t(\bs_i)$ is done using a univariate truncated normal likelihood with mean and standard deviation from the conditional multivariate normal distribution of $\widetilde{Y}_t(\bs)$.

@@

\subsection{Design}\label{sts:simdesign}
For all simulation designs, we generated data from model \eref{steq:partition} in \sref{sts:part} using $n_s=144$ sites and $n_t=50$ independent days.
The sites were generated uniformly on the square $[0, 10] \times [0, 10]$.
We generated data from five different simulation designs:
\begin{enumerate}[leftmargin=3em]
  \item Gaussian, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=5$ knots
  \item \Skewt, $K=1$ knots
  \item \Skewt, $K=5$ knots
  \item \citet{Reich2012} max-stable process %with GEV(1, 1, 0.2) marginals with dependence parameteter $\gamma_{\text{AL}} = 0.5$
  % \item Transformation below $T = q(0.80)$
  \item Brown-Resnick max-stable process \citep{Kabluchko2009} %with unit Fréchet marginals and stable semivariogram with range 1 and smoothness 0.5
\end{enumerate}
In the first three designs, the realizations from $v_t(\bs)$ were generated using a \Matern covariance with smoothness parameter $\nu = 0.5$, spatial range $\varphi = 1$ and $\gamma = 0.9$.
In the first design, $\sigma^2 = 2$ was used for all days which results in a Gaussian distribution.
For designs 2 and 3, $\sigma^2_{tk} \iid \text{IG}(3, 8)$ to give a $t$ distribution with 6 degrees of freedom.
For design 1, we set $\lambda = 0$.
For designs 2 and 3, $\lambda = 3$ was used as to simulate moderate skewness, and the $z_t$ were generated as described in \sref{sts:part}.
In designs 1 -- 3, the mean $\bX^\top \bbeta = 10$ was assumed to be constant across space.
In the fourth design, we generated from the max-stable model of \citet{Reich2012}.
The marginal distributions follow a generalized extreme value distribution with location parameter 1, scale parameter 1, and shape parameter 0.2.
Spatial dependence in the form an asymmetric logistic dependence function is induced by random effects for kernel basis functions associated with 144 spatial knots defined on a square grid on $[1,9] \times [1,9]$.
We set the dependence parameter ($\alpha$ in Reich and Shaby, 2012) to 0.5 which represents moderate spatial dependence.
For the final design, we generated data from a Brown-Resnick max-stable process  using \texttt{rmaxstab} in the \texttt{SpatialExtremes} package of \texttt{R} \citep{Ribatet2015}.
For this design we fixed unit \Frechet margins, and we used a range of 1 and smoothness 0.5.
% In the final design, we generate $\tilde{y}$ using the setting from design 2, and then transform the data
% \begin{align}
%   y = \left\{ \begin{array}{lc}
%     \tilde{y}, \quad & \tilde{y} > T \\[0.5em]
%     T \exp\{\tilde{y} - T\}, \quad & \tilde{y} \le T
%   \end{array}\right.
% \end{align}
% where $T = q(0.80)$ is the 80th sample quantile of the data.
% The final design is included to explore the importance of using a threshold exceedance model when the distribution for the bulk of the data is misspecified.

$M = 50$ data sets were generated for each design.
For each data set we fit the data using six models
\begin{enumerate}[leftmargin=3em]
  \item Gaussian marginal, $K=1$ knots
  \item \Skewt marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item \Skewt marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
  \item \citet{Reich2012} max-stable model thresholded at $T = q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
All methods were fit using a fully-Bayesian approach that simultaneously estimates marginal and spatial dependence parameters.
The design matrix $\bX$ includes an intercept with a first-order spatial trend with priors of $\beta_\text{int}$, $\beta_\text{lat}$, $\beta_\text{long},  \iid \text{N}(0, 10)$ although only the intercept is used in the data generation.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\varphi \sim \text{Unif}(0, 15)$.
The skewness parameter has prior $\lambda \sim N(0, 20)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(a / 2, b / 2)$, where $a$ has a discrete uniform prior on a mesh from $0.2$ to $20$ with spacing of $0.1$ and $b$ has a Gamma$(0.1, 0.1)$ prior.
As described in \sref{sts:skewt}, these priors are meant to be fairly uninformative to allow the data to dictate both the degrees of freedom $a$ and precision $b$ of the process.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We tried also fitting the \skewt marginals for the thresholded models, but it is very challenging for the MCMC to properly identify the skewness parameter with a censored left tail.
Each chain of the MCMC ran for 20,000 iterations which includes a burn-in period of 10,000 iterations.
Although the goal of this simulation study is not to assess parameter estimation, for design (2) and method (2) where data are generated and fit with a \skewt distribution, the samples converges for $\lambda$ and $a$, and the empirical coverage of posterior 95\% intervals is near the nominal level (96\% coverage for $\lambda$ and 90\% for $a$).
It should be noted that in the models with multiple partitions (i.e. models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC; however, we are not interested in these parameters but rather spatial predictions and tail probabilities which converge well.
Finally, we did not fit a Brown-Resnick model because we cannot use a Bayesian approach with so many sites.

@@

\section{Supplementary Materials}
Web Appendices, Tables, and Figures referenced in Sections 2.1, 2.2, 3.2, 3.3, 5.3, 6, and 6.2 are available with this paper at the Biometrics website on Wiley Online Library.
\texttt{R} code implementing the spatial \skewt model for threshold exceedances is available with this paper at the Biometrics website on Wiley Online Library.\vspace*{-8pt}
